---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Live Training

This is an empty repo for [Jared Lander's](https://www.jaredlander.com) Advanced Live Training.

# Clone this Repo

If you use git please clone this repo then open it as an [RStudio Project](https://support.rstudio.com/hc/en-us/articles/200526207-Using-Projects).

```{sh eval=FALSE}
# if using SSH
git clone git@github.com:jaredlander/LiveMarch2018.git

# if using https
git clone https://github.com/jaredlander/LiveMarch2018.git
```

If you don't use git, then please recreate this folder structure, and download `prep/DownloadData.r`, into the folder and open the `LiveMarch2018.Rproj` file using RStudio.

# Packages

To get started run the following code to install the latest version of the necessary packages.

```{r install.packages,eval=FALSE}
packages <- c('coefplot', 'data.world', 'DBI', 'doParallel', 'foreach', 
              'ggthemes', 'jsonlite', 'rprojroot', 'RSQLite', 'tidyverse', 
              'UsingR')
install.packages(packages)
```

# Data

Data for the class is kept at [data.world](https://data.world/landeranalytics/training).

They can be downloaded automatically using the following code. This script requires that you are using an [RStudio Project](https://support.rstudio.com/hc/en-us/articles/200526207-Using-Projects).

```{r source-data-file,eval=FALSE}
source('prep/DownloadData.r')
```

If you would like to download them manually you can create a free account at [data.world](https://www.data.wold].
