---
title: "My First Markdown Document"
author: "Jared P. Lander"
date: "March 8, 2018"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# First Section

We just created our first section in this document. Spacing is important in markdown, so we left a blank line after the hash tag. Adding a third sentence to comply with antiquated rules of grammar.

We created a new paragraph by leaving a blank line between text. This further shows how important spacing is in markdown.

# Second Section

To create a new section, simply start a new section with a hashtag. There is no need to close the old section.

# Let's Talk About Subsections

To create a subsection, use two hashtags.

## First Subsection

We now have a subsection in the enclosing section.

## Second Subsection

Just like with sections, we do not close a subsection, we just create a new one with two hashtags.

# Back to Sections

We create a new section, without closing the subsection, with a single hashtag just like before.

# Lists

## Unordered Lists

- Apples
- Bananas
- Oranges
- Kiwis

## Ordered Lists

1. New York
1. New Jersey
1. Detroit
1. Naples
1. Philadelphia
1. Rome

a. Coal
a. Wood
a. Gas

1. New York
    1. Coal
    1. Wood
    1. Gas
1. New Jersey
    1. Gas
1. Detroit
    1. Gas
1. Naples
    1. Wood
1. Philadelphia
1. Rome

# Formatting

_Emphasized Text_

__This will be strong text__

___This will be emphasized and strong___

`this is code`

# Links

[Link to my website](http://www.jaredlander.com)

# R Time!!!!!

```{r addition}
1 + 1
```

```{r variables}
x <- 3
x
```

```{r multiplication}
x*2
```

# Plots

```{r histogram, fig.cap='A histogram of diamond prices',fig.align='center'}
library(ggplot2)

ggplot(diamonds, aes(x=price)) + geom_histogram()
```

Now we see just the image, no code.

```{r histogram-carat, fig.cap='A histogram of carat', fig.align='center', echo=FALSE,warning=FALSE,message=FALSE}
ggplot(diamonds, aes(x=carat)) + geom_histogram()
```


